### 2019-09-09 paper/spad_single/sections/method.tex
Pushing through a bunch of random commits.

\paragraph{Differentiable Histogram Matching}
Given our initial depth map estimate, our goal is now to refine that depth map
so that it agrees with the information provided by the SPAD histogram.
Figure showing just the differentiable histogram matching part of the model.
At a high level, we perform local optimization over the pixels of the depth map
to make it consistent with the observed measurements $h[n]$.
Given per-pixel depth, we can simulate SPAD histogram formation using equation
\ref{global_hints}, where we approximate $\lambda_{x,y}[n]$ using kernel density
estimation \cite{something} as:
\begin{equation}
  \hat \lambda^{(i)}_{x,y}[n] = \frac{1}{\sigma\sqrt{2 \pi}}\exp\paren*{-\frac{1}{2\sigma^2}(n - \hat z^{(i)}(x,y))} \label{KDE}
\end{equation}
where $\hat z^{(i)}(x, y)$ is our estimate of the depth at pixel $(x,y)$ at
iteration $i$.

Once we have $\lambda^{(i)}$, we compute $\hat h[n]$ according to the rest of
the SPAD histogram formation model (neglecting the Poisson sampling) as follows
\begin{equation}
  \hat h[n] = \sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b. \label{diff_forward}
\end{equation}
Finally, given two histograms, we can compute the Wasserstein Distance between
them. As described in \ref{Cuturi et. al.}, the Wasserstein Distance or ``earth
mover's distance'' measures the distance between two probability distributions
by calculating the minimum cost of moving the mass required to turn the first
distribution into the second. It is particularly desirable
because unlike the KL divergence or the simple RMSE, the Wasserstein Distance scales with
separation as well as magnitude (see figure). Although the computation of the
Wasserstein Distance requires solving a linear program, there is a regularized
version known as the dual-Sinkhorn Distance
which can be computed via Sinkhorn-Knopp Iterations in a fast and differentiable manner.
We refer the reader to \ref{Cuturi et. al.} for details, but provide the
optimization problem here.

Given histograms $h, \hat h$ in $\Delta^n$ and a cost matrix $C$ in $\R^{n \times
  n}$, the dual-Sinkhorn Divergence is found by solving
the optimization problem
\begin{equation}
    \begin{aligned}
    &\text{minimize} && \langle W, C \rangle  - \frac{1}{\lambda}h(W) \\
    &\text{subject to} && W^Th = \bm{1} \\
    &                  && W\hat h = \bm{1} \\
    &                  && W \succeq 0 \\
  \end{aligned}
\end{equation}
where $W \in \Delta^{n \times n}$ is the optimization variable, $\bm{1}$ denotes the
vector of all ones, $h(\cdot)$ is the entropy of a probability distribution, and
$\langle \cdot, \cdot \rangle$ denotes the inner product of two matrices.
\begin{itemize}
\item Pseudocode for sinkhorn iterations?
  \item Not sure what figure to use...
\end{itemize}
\newpage
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/full_pipeline/full_pipeline.png}
  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
  per-pixel depth estimate. We then perform gradient descent to optimize that
  estimate using the SPAD forward model and the dual-Sinkhorn distance.}
\end{figure}

\subsection{Implementation Details}
For the Monocular Depth Estimator, we use a pretrained version of the
the Deep Ordinal Regression Network (DORN) \cite{}. We use the implementation of
the Sinkhorn Iteration (for calculating the dual-Sinkhorn distance)
from \ref{Cuturi et. al.} We update the depth map using gradient descent.
Everything is implemented in PyTorch.
We run the model on a NVIDIA Titan X GPU, where it takes approximately 5 seconds
to fully process a single RGB-SPAD data pair.
Table with hyperparameters (defer to supplementary info?)
\begin{itemize}
\item Kernel Density Estimation (sigma)
\item Sinkhorn Iterations (maximum number, epsilon tolerance)
\item Gradient Descent (learning rate, epsilon tolerance, max iterations)
\item Simulation hyperparameters ($\eta, b$)
\end{itemize}

>>>>

\paragraph{SPAD Denoising}
\begin{itemize}
  \item Discuss MLE for SPAD denoising
  \item Write optimization problem for SPAD denoising
  \item Show performance on a few examples 
\end{itemize}
\paragraph{Exact Histogram Matching}
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/full_pipeline/full_pipeline.jpeg}
  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
  per-pixel depth estimate. We then perform gradient descent to optimize that
  estimate using the SPAD forward model and the dual-Sinkhorn distance
  .}
\end{figure}
An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
pixels of the image whose value lies in the range $[b_i, b_i+1)$.
Then, given a source image $S$ with histogram $(h_s, b)$ and a target histogram
$(h_t, b)$, histogram matching generates a new image $M$ such that $h_m \approx
h_t$ and the pixel values in $M$ are in the same relative order as in $S$.

\subsection{Implementation Details}
For the Monocular Depth Estimator, we use pretrained versions of the
the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
The exact histogram matching method is as described in \cite{}.
